---
output:
  pdf_document: default
  theme: null
  bg: "#121212"
  fg: "#E4E4E4"
  base_font: null
  google: Prompt
  html_document: null
---

### R-code notes compilation for Week 6, February 22th and 25th

##### Compiled by: Prognadipto Majumder, B.Math(hons.) 1st year

```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE)
library(ggplot2)
```

```{r}
runningmean <- function(x, N) {
  y <- sample(x, N, replace = TRUE)
  # THIS samples N points wih replacement
  c <- cumsum(y)
  # cumulative sums of the 1st i values in i th position
  n <- 1:N
  c / n
  # Division is vectorised, mean of 1st i values of y is in ith position
}
```

$$\\[0.5in]$$

Simulating $1000$ trials of $Ber(\frac{1}{2})$

The $1000$ $Ber(\frac{1}{2})$ variables being $X_1,X_2, \ldots ,X_{1000}$,

```{r}
u <- runningmean(c(0, 1), 1000)
```

The function returns the mean of the first $i$ random variables in the $i^{th}$ place.
, i.e., `u[i]` = $\frac{X_1+X_2+...+X_i}{i}$

We "guess" the value of `u[i]` will converge to $\frac{1}{2}$ as `i` gets really large. (It should converge with probability $1$)

$$\\[0.5in]$$

Plotting line graph in `ggplot`

```{r}
x <- 1:1000
data <- data.frame(u,x)

ggplot(data) +
  geom_line(aes(x = x, y = u))
```

Printing 10 line graphs in the same plot by replicate command that makes 10 function calls. For each call, we RANDOMLY assign a colour to graph.

```{r}
df <- data.frame(replicate(10,runningmean(c(0, 1), 1000), x))

ggplot(df, mapping = aes(colour = rgb(runif(3), runif(3), runif(3)))) +
  geom_line()
```
